\addcontentsline{toc}{chapter}{\MakeUppercase{acknowledgement}\vspace{-0.5cm}}

\begin{center}
	\noindent \textbf{ACKNOWLEDGEMENT}
\end{center}

My heartfelt thanks go to the following individuals for their invaluable contributions to the completion of this study and to my roller coaster master's journey:

First and foremost, to my adviser and co-adviser, Prof. Carl John O. Salaan and Prof. Earl Ryan M. Aleluya, for their unwavering support, direction, motivation, and guidance throughout this research journey. I also extend my gratitude to my panels, Prof. Alindayo and Prof. Bahinting, for their invaluable inputs and suggestions, which helped me refine my research significantly.

I am deeply thankful to my classmates, Nouran Usman, Melody Mae Maluya, Jamaica Mae Pepito, Collien Princess Pepito, Ryan Himongala, and Rochelle Madulara, for their support, laughter, memorable travels, and cherished memories. A special thanks to the Control and Robotics Laboratory family: ma'am Jam, sir Imman, kuya Joey, ma'am Pao, and sir Steve, for their assistance and contributions.

I am also grateful to my Dormitory family, too many to mention individually, for our bonding, support, and the countless memories we shared.

I extend my sincere thanks to the Department of Science and Technology - Engineering Research and Development for Technology for their financial support, with a special mention to Ma'am Doruthee for processing our allowances and addressing other financial and scholar concerns.

Most importantly, I owe a profound debt of gratitude to my ina (mother) and ama (father), Maryam Omar and Usman Omar Jr., for their unconditional love, understanding, care, moral support, and prayers.

Above all, I thank Allah the Mighty and the Majestic for His guidance and for bestowing upon me the knowledge, wisdom, patience, and strength required to complete this work.

\vspace{0.5cm}

\begin{flushright}
	Jaafar J. Omar
\end{flushright}

\vspace{0.5cm}